### 2025-08-12 download-football-data.qmd
20250812 - linked figures

>>>>

You can download fantasy football projections in `R` using the `ffanalytics::scrape_data()` function of the `ffanalytics` package [@R-ffanalytics].
Alternatively, if you prefer a graphical user interface, you can also download fantasy football projections using the Fantasy Football Analytics web application (depicted in @fig-projectionsTabFFA): <https://apps.fantasyfootballanalytics.net>.

::: {#fig-projectionsTabFFA}
[![](images/projectionsTab.png){fig-alt="Fantasy Football Projections Available From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}](https://apps.fantasyfootballanalytics.net)

Fantasy Football Projections Available From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>.
:::

### 2025-08-12 draft.qmd
20250812 - linked figures

::: {#fig-snakeDraftToolFFA}
![](images/snakeDraftTool.png){fig-alt="Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>."}

Free Snake Draft Tool From Fantasy Football Analytics. From <https://apps.fantasyfootballanalytics.net>.
:::

@@

::: {#fig-auctionDraftToolFFA}
![](images/lineupOptimizer.png){fig-alt="Free Auction Draft Lineup Optimizer From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}

>>>>

::: {#fig-snakeDraftToolFFA}
[![](images/snakeDraftTool.png){fig-alt="Free Snake Draft Tool From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}](https://apps.fantasyfootballanalytics.net)

Free Snake Draft Tool From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>.
:::

@@

::: {#fig-auctionDraftToolFFA}
[![](images/lineupOptimizer.png){fig-alt="Free Auction Draft Lineup Optimizer From Fantasy Football Analytics: <https://apps.fantasyfootballanalytics.net>."}](https://apps.fantasyfootballanalytics.net)
